Towards Transparency and Open Science

### 2023-01-05 manuscript.Rmd
correct integral
add some notational things

Information theory provides a rigorous mathematical measure that can be understood as the verisimilitude of a theory.
That is, how much information about the truth is lost when the theory is used to model reality.
Expressed mathematically, we have a function $f(x)$ that gives us the liklihood to observe the state of the world $x$ where $f$ represents the ground truth.
We are now interested in how much information is lost if we use $g(x)$, our theory, instead of $f(x)$, the reality, over all possible states $\mathcal{X}$.
Expressed as lost bits of information, a measure known as Kullback–Leibler divergence [@kullbackInformationSufficiency1951], we get:

@@

$$
\mathcal{L}_{KL}(f, g) =\int_{\mathcal{X}}f(x)\log\left(g(x)^{-1}\right) - \int_{\mathcal{X}}f(x)\log\left(f(x)^{-1}\right)
$$

$$
\mathcal{L}_{KL}(f, g) = \mathbb{E}_{X \sim f}\left[\log(f(x))\right] - \mathbb{E}_{X \sim f}\left[\log(g(x))\right]
$$

>>>>

Information theory provides a rigorous mathematical measure that can be understood as the verisimilitude of a theory.
That is, how much information about the truth is lost when the theory is used to model reality.
Expressed mathematically, we have a random variable $X ~ f$, with values in $\mathcal{X}$, where the distribution $f$ represents the ground truth.
We are now interested in how much information is lost if we use $g$, our theory, instead of $f$, the reality, to approximate $X$ over all possible states $\mathcal{X}$.
Expressed as lost bits of information, a measure known as Kullback–Leibler divergence [@kullbackInformationSufficiency1951], we get:

@@

\begin{align}
\mathcal{L}_{KL}(f, g) &= \int_{\mathcal{X}}f(x)\log\left(f(x)\right) - \int_{\mathcal{X}}f(x)\log\left(g(x)\right)\\
 &= \mathbb{E}_{X \sim f}\left[\log(f(x))\right] - \mathbb{E}_{X \sim f}\left[\log(g(x))\right]
\end{align}
